\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2022-05-17 doc/USER_MANUAL/11_graphics.tex
adds option (MOVIE_TYPE == 3) for shakemap to output geometric mean of horizontal PG-values

You can also output shakemaps independant of the \texttt{MOVIE\_SURFACE} flag. Shakemaps show the peak-ground values of the simulation. For creating shakemaps (at the end of the simulation), you would set the parameter
\texttt{\small CREATE\_SHAKEMAP} to \texttt{\small .true.}.
For shakemaps, both the parameters \texttt{\small MOVIE\_TYPE} and \texttt{\small USE\_HIGHRES\_FOR\_MOVIES} affect the output. The following setting has an additional affect:
\begin{itemize}
\item \texttt{\small MOVIE\_TYPE}: if set to $1$, the horizontal peak-ground values of displacement/velocity/acceleration are output. if set to $2$, the maximum length of the particle displacement/velocity/acceleration vector is output. Please be aware that these peak-ground values can differ from each other.
\end{itemize}

>>>>

You can also output shakemaps independant of the \texttt{MOVIE\_SURFACE} flag. Shakemaps show the peak-ground values of the simulation. For creating shakemaps (at the end of the simulation), you would set the parameter
\texttt{\small CREATE\_SHAKEMAP} to \texttt{\small .true.}.
For shakemaps, both the parameters \texttt{\small MOVIE\_TYPE} and \texttt{\small USE\_HIGHRES\_FOR\_MOVIES} affect the output. The following setting has an additional affect:
\begin{itemize}
\item \texttt{\small MOVIE\_TYPE}: if set to $1$, the horizontal peak-ground values of displacement/velocity/acceleration are output; if set to $2$, the maximum length of the particle displacement/velocity/acceleration vector is output; if set to $3$, the geometric mean of horizontal peak-ground values of displacement/velocity/acceleration are output. Please be aware that these peak-ground values can differ from each other.
\end{itemize}
